\cvsection{conference papers}
\cvpublication{
    \begin{enumerate}[resume]
        \setcounter{enumi}{\value{pubs}}
        \item {
        J.R. Leonard, A.A. High, \textbf{A.T. Hammack}, M.M. Fogler, L.V. Butov, K.L. Campman, and A.C. Gossard.
       Pancharatnam-Berry phase in a condensate of indirect excitons.
        \\ \href{https://doi.org/10.1364/CLEO_QELS.2018.FM3H.3}{doi:10.1364/CLEO\_QELS.2018.FM3H.3}
        }
        \item {
        L.M. Otto, \textbf{A.T. Hammack}, S. Aloni, D.F. Ogletree, D.L. Olynick, S. Dhuey, B.J.H. Stadler, and A.M. Schwartzberg.
        Plasma-enhanced atomic layer deposition for plasmonic TiN. 
        Proceedings Volume 9919, Nanophotonic Materials XIII, 99190N (2016).
        \\ \href{https://doi/org/10.1117/12.2238340}{doi:10.1117/12.2238340}
        }
        \item {
        L.M. Otto, E.A. Gaulding, C.T. Chen, T. Kuykenda, A. Zykov, \textbf{A.T. Hammack}, F.M. Toma, D.F. Ogletree, S. Aloni, B.J.H. Stadler, and A.M. Schwartzberg.
        Three-dimensional titanium nitride plasmonics with plasma-enhanced atomic layer deposition. 
        The 8th International Conference on Surface Plasmon Photonics (SPP8) (2017).
        }
        \item {
        M. Remeika, \textbf{A.T. Hammack}, S. Poltavtsev, J. Wilkes, A. Ivanov, M. Hanson, and A.C. Gossard.
        Pattern formation in the exciton inner ring.
        CLEO: 2013 OSA Technical Digest (online) (Optical Society of America, 2013), paper QM2D.6.
        \\ \href{https://doi.org/10.1364/CLEO_QELS.2013.QM2D.6}{doi:10.1364/CLEO\_QELS.2013.QM2D.6}
        }
        \item {
        M. Vladimirova, A.A. High, A.T. Hammack, J.R. Leonard, Sen Yang, L.V. Butov, T. Ostatnický, A. Kavokin, A.C. Gossard, T.C.H. Liew, and K.L. Campman.
        Spin currents in a coherent exciton gas.
        PLMCN 14 (2013).
        \\ \href{https://hal.archives-ouvertes.fr/hal-00835599}{hal-00835599}
        }
        \item {
        Y.Y. Kuznetsova, M. Remeika, A.A. High, A.T. Hammack, L.V. Butov, M. Hanson, and A.C. Gossard.
        All-optical excitonic switch. 
        CLEO 2010 OSA Technical Digest (CD) (Optical Society of America, 2010), paper QFI1.
        \\ \href{https://doi.org/10.1364/QELS.2010.QFI1}{doi:10.1364/QELS.2010.QFI1}
        }
        \item {
        G. Grosso, J.C. Graves, \textbf{A.T. Hammack}, A.A. High, L.V. Butov, M. Hanson, and A.C. Gossard.
        Excitonic switches operating at around 100 K.
        CLEO 2010 OSA Technical Digest (CD) (Optical Society of America, 2010), paper QFI5.
        \\ \href{https://doi.org/10.1364/QELS.2010.QFI5}{doi:10.1364/QELS.2010.QFI5}
        }
        \item {
        \textbf{A.T. Hammack}, L.V. Butov, J. Wilkes, L. Mouchliadis, E.A. Muljarov, A.L. Ivanov, and A.C. Gossard.
        Spatially resolved kinetics and spatially separated pump-probe studies of transport and thermalization of indirect excitons.
        CLEO 2010 OSA Technical Digest (CD) (Optical Society of America, 2010), paper QFI7.
        \\ \href{https://doi.org/10.1364/QELS.2010.QFI7}{doi:10.1364/QELS.2010.QFI7}
        }
        \item {
        J. Wilkes, L. Mouchliadis, E.A. Muljarov, A.L. Ivanov, \textbf{A.T. Hammack}, L.V. Butov, and A.C. Gossard.
        Dynamics of the inner ring in photoluminescence of GaAs/AlGaAs indirect excitons. 
        International Conference on Optics of Excitons in Conﬁned Systems (OECS11), J. of Phys.: Conf. Series 210, 012050 (2010).
        \\ \href{https://doi.org/10.1088/1742-6596/210/1/012050}{doi:10.1088/1742-6596/210/1/012050}
        }
        \item {
        \textbf{A.T. Hammack}, Sen Yang, L.V. Butov, and A.C. Gossard. 
        Properties of the exciton inner ring at ultra-low temperatures and high magnetic ﬁelds, 
        in CLEO/IQEC, OSA Technical Digest (CD) (Optical Society of America, 2009), paper ITuH4.
        \\ \href{https://doi.org/10.1364/IQEC.2009.ITuH4}{doi:10.1364/IQEC.2009.ITuH4}
        }
        \item {
        \textbf{A.T. Hammack}, L.V. Butov, L. Mouchliadis, L.E. Smallwood, A.L. Ivanov, and A.C. Gossard. 
        Kinetics of excitons in an optically-induced exciton trap.
        CLEO/QELS Conference and Photonic Applications Systems Technologies, OSA Technical Digest (CD) (Optical Society of America, 2008), paper QThI2. 
        }
        \item {
        A.A. High, A.K. Thomas, \textbf{A.T. Hammack}, L. Butov, M. Hanson, and A. Gossard. 
        A diamond trap for indirect excitons in coupled quantum wells.
        CLEO/IQE Conference, OSA Technical Digest (CD) (Optical Society of America, 2009), paper IThE5.
        }
        \item {
        A.A. High, \textbf{A.T. Hammack}, L. Butov, L. Mouchliadis, A. Ivanov, M. Hanson, and A.C. Gossard. 
        Interaction and cooling of the indirect excitons in elevated traps.
        CLEO/QELS Conference and Photonic Applications Systems Technologies, OSA Technical Digest (CD) (Optical Society of America, 2008), paper QThE2.
        }
        \item {
        Sen Yang, \textbf{A.T. Hammack}, A.V. Mintsev, M.M. Fogler, L.V. Butov, L.S. Levitov, B.D. Simmons, and A.C. Gossard.
        Spontaneous coherence, interaction and kinetics of macroscopically ordered exciton state.
        CLEO/QELS Conference and Photonic Applications Systems Technologies, OSA Technical Digest (CD) (Optical Society of America, 2008), paper QThI1. 
        \setcounter{pubs}{\value{enumi}}
        }
    \end{enumerate}
}