\cvsection{conference abstracts}
\cvpublication{
    \begin{enumerate}
        \setcounter{enumi}{\value{pubs}}
        \item {
        K. Gilmore, \textbf{A. Hammack}, A. Sawvel, E. Rosen, D.F. Ogletree, J. Urban, D. Milliron, B. Helms, B. Cohen, and D. Prendergast.
        First-principles spectroscopic characterization of PbSe nanoparticles passivated with Fe Complexes.
        Bulletin of The American Physical Society March Meeting 57 (2012).
        }
        \item {
        J. Leonard, A. Winbow, M. Remeika, Y. Kuznetsova, A. High, \textbf{A. Hammack}, L. Butov, J. Wilkes, A. Guenther, A. Ivanov, M. Hanson, A. Gossard. 
        Excitons in moving lattices.
        Bulletin of The American Physical Society March Meeting 56 (2011).
        }
        \item {
        K. Gilmore, \textbf{A. Hammack}, A. Sawvel, E. Rosen, D.F. Ogletree, J. Urban, D. Milliron, B. Helms, B. Cohen, and D. Prendergast.
        Characterization of the surface environment of PbSe nanoparticles by correlating calculated and measured x-ray spectra.
        Bulletin of The American Physical Society March Meeting 56 (2011).
        }
        \item {
        Sen Yang, \textbf{A.T. Hammack}, A.V. Mintsev, E.E. Novitskaya, L.V. Butov, L.S. Levitov, B.D. Simmons, and A.C. Gossard.
        Spontaneous coherence, interaction and kinetics of macroscopically ordered exciton state.
        Fundamental Optical Processes in Semiconductors 3 (2007).
        }
        \item {
        A.A. High, \textbf{A. Hammack}, E.E. Novitskaya, L. Butov, A. Gossard, and M. Hanson.
        Control of exciton ﬂux through tunable potential reliefs.
        Fundamental Optical Processes in Semiconductors 3 (2007).
        }
        \item {
        Sen Yang, \textbf{A.T. Hammack}, M.M. Fogler, L.V. Butov, and A.C. Gossard.
        Coherence length of cold exciton gases in coupled quantum wells.
        Bulletin of The American Physical Society March Meeting 52 (2007).
        }
        \item {
        Sen Yang, \textbf{A.T. Hammack}, L.V. Butov, and A.C. Gossard.
        Spontaneous ﬁrst-order optical coherence in cold exciton gases in coupled quantum wells.
        Bulletin of The American Physical Society March Meeting 51 (2006).
        }
        \item {
        Sen Yang, \textbf{A.T. Hammack}, L.V. Butov, L.S. Levitov, B.D. Simons, and A.C. Gossard.
        Characterization of macroscopic ordering in exciton rings.
        Bulletin of The American Physical Society March Meeting 50 (2005).
        }
        \item {
        K. Nagoaka, M. Comstock, \textbf{A. Hammack}, and M.F. Crommie.
        Observation of Band-Bending at the Bare Si (100) Surface Using STM Spectroscopy.
        Bulletin of The American Physical Society March Meeting 48 (2003).
        }
        \item {
        M. Comstock, K. Nagoaka, \textbf{A. Hammack}, and M.F. Crommie.
        STM spectroscopic measurements of indium nanowires on Si(100).
        Bulletin of The American Physical Society March Meeting 48 (2003).
        }
        \setcounter{pubs}{\value{enumi}}
    \end{enumerate}
}