\cvsection{entrepreneurial experience}
\begin{cventries}
    \cventry
    {Principal Scientist}
    {Locus Biosciences}
    {Research Triangle Park, NC}
    {2018.08 -- Present}
    {
      \begin{cvitems}
        Principal scientist and management team member following acquisition of EpiBiome by Locus Biosciences. Responsible for machine learning and artificial intelligence efforts, laboratory information management systems, data science, advanced liquid handling technology development, as well as continued assistance in fundraising and business development.
      \end{cvitems}
    }
    \cventry
    {Managing Partner, Physicist}
    {LCFTA}
    {Austin, TX}
    {2018.08 -- Present}
    {
      \begin{cvitems}
        Managing Partner for LCFTA, a science, engineering, and executive consulting firm advising small companies focused on translational research and development activities in the biotechnology, quantum computing, materials, optical physics, and information science disciplines.
      \end{cvitems}
    }
    \cventry
    {Co-developer, Advisor}
    {Laminera}
    {Berkeley, CA}
    {2017.03 -- Present}
    {
      \begin{cvitems}
        Co-developer of synthetic metal deposition technologies for Laminera, an early-phase startup admitted into cohort three of Cyclotron Road, the LBNL energy science accelerator program.
      \end{cvitems}
    }
    \cventry
    {Co-founder, Board member, Chief Financial Officer}
    {Dimensional Industries}
    {Austin, TX}
    {2018.06 -- PRESENT}
    {
      \begin{cvitems}
        Board member and Chief Financial Officer in charge of brokering a licensing or acquisition deal for a rapid-device-prototyping, biosensing, and real-time artificial intelligence IP portfolio.
      \end{cvitems}
    }
    \cventry
    {Co-founder, Chief Executive Officer, Board Member}
    {EpiBiome}
    {Union City, CA / Austin, TX}
    {2018.01 -- 2018.12}
    {
      \begin{cvitems}
        Co-founder of EpiBiome, a 25+ person venture-backed biotechnology company tackling the emerging threat of antibiotic-resistant bacterial strains using next-generation sequencing technologies and bacteriophage-based antimicrobials. Principal investigator for bioinformatics, data science, and sequencing technology development. Presided over the negotiation and acquisition of EpiBiome by Locus Biosciences, along with the successful delivery of the EpiBiome phage discovery platform to Locus.
      \end{cvitems}
    }
    \cventry
    {Co-founder, Chief Operations Officer, Board Member}
    {EpiBiome}
    {South San Francisco, CA / Austin, TX}
    {2013.11 -- 2017.12}
    {
      \begin{cvitems}
        Prior to taking on CEO role, was Chief Operations Officer and the principal investigator for bioinformatics, data science, and sequencing technology development.
      \end{cvitems}
    }
    \cventry
    {Co-founder, Board member}
    {Dimensional Industries}
    {Oakland, CA}
    {2012.06 -- 2014.04}
    {
      \begin{cvitems}
       Co-founder for rapid device prototyping, biosensing, and real-time artificial intelligence product design company.
      \end{cvitems}
    }
    \cventry
    {Co-founder, President, Treasurer, Lead Circuit Design Engineer}
    {Halide Design}
    {San Diego, CA / Oakland, CA}
    {2007.07 -- 2012.07}
    {
      \begin{cvitems}
        Co-founder of Halide Design, a boutique high-end audio design firm and audio equipment manufacturer that won numerous accolades in audio industry magazines such as Stereophile, AudioStream, and The Audio Beat.
      \end{cvitems}
    }
\end{cventries}
