\cvsection{selected talks}
\cvpublication{
    \begin{enumerate}
        \setcounter{enumi}{\value{pubs}}
        \item {
        \textbf{A.T. Hammack}. 
        High throughput discovery for bacteriophage based therapeutics.
        The 3$\mathsf{^{rd}}$ Innovator's Forum on Human Microbiome (2018).
        }
        \item {
        \textbf{A.T. Hammack}. 
        The growing threat of antibiotics resistance, and the use of microbial surveillance and bacteriophage based therapeutics to combat the trend.
        Cycltron Road Seminar Series (2018).
        }
        \item {
        \textbf{A.T. Hammack}. 
        The growing threat of antibiotics resistance, and the use of microbial surveillance and bacteriophage based therapeutics to combat the trend.
        Molecular Foundry Seminar Series (2017).
        }
        \item {
        \textbf{A.T. Hammack}.
        Next-generation antibacterials: Combating infectious disease with phage technology.
        CUBE Tech Fair Berlin (2017).
        }
        \item {
        \textbf{A.T. Hammack}.
        Coherence in exciton gases.
        Workshop on Quantum Coherence in Energy Conversion University of Freiburg (2011).
        }
        \item {
        \textbf{A.T. Hammack}.
        Cold exciton gases in coupled quantum wells.
        Molecular Foundry Weekly Seminar Series (2009).
        }
        \item {
        \textbf{A.T. Hammack}, L.V. Butov, L. Mouchliadis, L.E. Smallwood, A.L. Ivanov, and A.C. Gossard.
        Kinetics of cold excitons in the laser-induced exciton trap.
        Bulletin of The American Physical Society March Meeting 52 (2007).
        }
        \item {
        \textbf{A.T. Hammack}, M. Griswold, L.V. Butov, L.E. Smallwood, A.L. Ivanov, and A.C. Gossard.
        Laser induced trapping of excitons in coupled quantum wells.
        Bulletin of The American Physical Society March Meeting 51 (2006).
        }
        \item {
        \textbf{A.T. Hammack}, G.O. Andreev, Sen Yang, N.A. Gippius, and L.V. Butov.
        Exciton conﬁnement in traps formed by a laterally modulated gate voltage.
        Bulletin of The American Physical Society March Meeting 50 (2005).
        }
        \setcounter{pubs}{\value{enumi}}
    \end{enumerate}
}